### 2016-07-13 Projects/DelCo_2012/Report/DelCo_2012.tex
minor updates to report

Rekindling and the impact of the second nozzle can been seen in the time-temperature data of thermocouples within the fire room. Figure~\ref{fig:fs_instruments} shows the positions of thermocouple arrays TC A1 and TC A2. Note that TC A1 is closer to fuel and ignition.

@@

For the first comparison tests in the series, CAF~1 and Water~1, the thermocouple data from TC A2 is shown in Figs.~\ref{fig:caf1_tca2} and \ref{fig:water1_tca2}, respectively. From the figures, the impact of the first suppression event (hallway nozzle on) is evident from the sharp decline in thermocouple temperatures.

>>>>

Rekindling and the impact of the second nozzle can been seen in the time-temperature data of thermocouples within the fire room. Figure~\ref{fig:fs_instruments} shows the positions of thermocouple arrays TC A1 and TC A2. Note, TC A1 is closer to fuel and ignition.

@@

For tests CAF~1 and Water~1, the thermocouple data from TC A2 is shown in Figs.~\ref{fig:caf1_tca2} and \ref{fig:water1_tca2}, respectively. From the figures, the impact of the first suppression event (hallway nozzle on) is evident from the sharp decline in thermocouple temperatures. After the first suppression, there is an increase in temperature at position TC A2 as high temperature gases from a rekindle of the fire flow toward the low pressure structure exit. The second suppression (doorway nozzle) further dropped the temperature for both water and CAF. The remainder of the fire suppression test data is included in Appendix~\ref{app:fire_suppression}.
